### 2023-01-27 paper.Rmd
word count
typos

author:
  - name          : "Martin Papenberg"
    affiliation   : "1"
    corresponding : yes
    address       : "Heinrich Heine Universität Düsseldorf,  Institut für Experimentelle Psychologie, Universitätsstraße 1, 40225 Düsseldorf, Germany"
    email         : "martin.papenberg@hhu.de"

@@

keywords          : "Anticlustering, k-means, k-plus, variance, covariance, skewness, kurtosis, stimulus selection"
wordcount         : "5114"

@@

Generally, it should be noted that diversity anticlustering is a good all-arounder method that tends to address all distribution characteristics. For the specific objectives that are addressed by the k-plus methods, however, diversity anticlustering was outperformed. As as side note, apart from k-plus correlation, diversity anticlustering was the only method that equalized correlation structure among groups. To the best of my knowledge, this observation has not been made previously, even though the maximum diversity problem has been widely studied.

@@

The function call takes about 10 seconds on a contemporary personal computer. The function `kplus_anticlustering()` has four boolean arguments to specify whether variance, skewness, kurtosis and covariances should be included as part of the k-plus criterion. Only the argument `variance` is set to `TRUE` by default---corresponding to the understanding that k-plus is an extension to k-means that at least equalizes variances in addition to means. The arguments corresponding to skewness, kurtosis and convariance have to be spefically "turned on", i.e., by setting them to `TRUE` in the function call of `kplus_anticlustering()`. If other higher order moments should be included as part of the optimization, the optional argument `moments` can be used to specify the desired moments as an integer vector. The argument `method = "local-maximum"` ensures that the k-plus criterion is optimized using the local maximum search method described in the previous section. The argument `K` describes the number of groups. By default, the function ensures that all features are standardized before the optimization starts; in particular, this option enforces that all k-plus criteria receive the same weight during the optimization process. This behaviour can be adjusted using the boolean argument `standardize`.

@@

A simulation study and examples on real norming data showed that the k-plus criterion is well-suited to maximize between-group similarity with regard to multiple criteria. Given that similarity with regard to variances was achieved with almost no sacrifice to similarity in means, k-plus anticlustering should be considered as the default replacement of classical k-means when striving for between-group similarity.[^binarydata] The results did however show that fulfilling multiple criteria at the same time can be challenging in small data sets. In practice, users can try out different objectives and see which specification fulfills their needs. A reasonable approach is to start "greedy", e.g. by specifying that multiple distribution moments should equalized. If the results of such a greedy setup are subpar, users can reduce their requirements by opting for fewer criteria (e.g., only the mean and variance). Using the open source R package `anticlust`, the (repeated) application of k-plus anticlustering is easily accessible and free.

>>>>

author:
  - name          : "Martin Papenberg"
    affiliation   : "1"
    corresponding : yes
    address       : "Heinrich-Heine-Universität Düsseldorf,  Institut für Experimentelle Psychologie, Universitätsstraße 1, 40225 Düsseldorf, Germany"
    email         : "martin.papenberg@hhu.de"

@@

keywords          : "Anticlustering, k-means, k-plus, variance, covariance, skewness, kurtosis, stimulus selection"
wordcount         : "4992"

@@

Generally, it should be noted that diversity anticlustering is a good all-rounder method that tends to address all distribution characteristics. For the specific objectives that are addressed by the k-plus methods, however, diversity anticlustering was outperformed. As as side note, apart from k-plus correlation, diversity anticlustering was the only method that equalized correlation structure among groups. To the best of my knowledge, this observation has not been made previously, even though the maximum diversity problem has been widely studied.

@@

The function call takes about 10 seconds on a contemporary personal computer. The function `kplus_anticlustering()` has four boolean arguments to specify whether variance, skewness, kurtosis and covariances should be included as part of the k-plus criterion. Only the argument `variance` is set to `TRUE` by default---corresponding to the understanding that k-plus is an extension to k-means that at least equalizes variances in addition to means. The arguments corresponding to skewness, kurtosis and covariance have to be specifically "turned on", i.e., by setting them to `TRUE` in the function call of `kplus_anticlustering()`. If other higher order moments should be included as part of the optimization, the optional argument `moments` can be used to specify the desired moments as an integer vector. The argument `method = "local-maximum"` ensures that the k-plus criterion is optimized using the local maximum search method described in the previous section. The argument `K` describes the number of groups. By default, the function ensures that all features are standardized before the optimization starts; in particular, this option enforces that all k-plus criteria receive the same weight during the optimization process. This behaviour can be adjusted using the boolean argument `standardize`.

@@

A simulation study and examples on real norming data showed that the k-plus criterion is well-suited to maximize between-group similarity with regard to multiple criteria. Given that similarity with regard to variances was achieved with almost no sacrifice to similarity in means, k-plus anticlustering should be considered as the default replacement of classical k-means when striving for between-group similarity.[^binarydata] The results did however show that fulfilling multiple criteria at the same time can be challenging in small data sets. In practice, users can try out different objectives and see which specification fulfills their needs. A reasonable approach is to start "greedy", e.g. by specifying that multiple distribution moments should equalized. If the results of such a greedy setup are not satisfying, users can reduce their requirements by opting for fewer criteria (e.g., only the mean and variance). Using the open source R package `anticlust`, the (repeated) application of k-plus anticlustering is easily accessible and free.
